Revision of MS #2018:11:32569:0:0:REVIEW

### 2019-01-30 docs/Manuscript.tex
Proof-read and added the LaTexDiff version of the marked up MS

\begin{abstract}
Lionfish (\textit{Pterois volitans / miles}) are an invasive species in
the Western Atlantic and the Caribbean. Improving management of invasive
lionfish populations requires accurate total biomass estimates, which
depend on accurate estimates of allometric growth. Sedentary species
like lionfish often exhibit high levels of spatial variation in life
history characteristics. We review 17 published length-weight
relationships for lionfish taken throughout their invasive range and
found significant regional differences in allometric growth parameters.
The spatial pattern we observed is consistent with findings from other
studies focusing on genetics or length-at-age. We show that the use of
\textit{ex situ} parameters can result in up to a threefold under- or
overestimation of total weight, but using parameters from nearby regions
reduces this error. These findings can have substantial implications for
management in terms of predicting effects on local ecosystems,
evaluating the effectiveness of removal programs, or estimating biomass
available for harvest.
\end{abstract}

@@

Outcomes of previous studies suggest lionfish are likely to exhibit
spatial heterogeneity in the length-weight relationship, which we
summarize in two main causes. First, culling programs are effective in
reducing local adult populations largely because lionfish exhibit high
levels of site fidelity and small home ranges
\citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}. It is known
that fish with sedentary behavior are likely to exhibit high levels of
spatial variation in important life history characteristics such as
growth or natural mortality rates
\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. Second,
genetic analysis of lionfish suggests biological differences due to the
existence of two genetically distinct invasive subpopulations between
the Western Atlantic and the Caribbean \citep{betancurr_2011}. The large
number of site-specific studies reporting the length-weight relationship
of lionfish provide variable estimates. These differences may be
increasingly important when estimating the potential effectiveness of
lionfish culling programs
\citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
extent to which using \emph{ex situ} parameters to estimate total weight
from length observations remains unexplored.

@@

We reviewed 12 published studies and obtained 17 length-weight
relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7),
and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}). We
collected information on sampling methods, sex differentiation,
location, and depth ranges from each study when available. Only two
studies reported parameters for each gender
\citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were
included in a study if gender was unspecified. Reviewed studies
presented information for organisms obtained at depths between 0.5 m and
57 m. Four studies explicitly stated that their organisms were sampled
with pole spears
\citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six
studies mentioned that some of their organisms were obtained with pole
spears (or other type of harpoon) but also hand-held nets or fish traps
\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016},
and two studies did not specify how organisms were sampled
\citep{darling_2011,deleon_2013}.

@@

Some of the reviewed studies inconsistently defined \(a\) as either the
ponderal index from Eq. \ref{eq:allometric} or the y-intercept from the
linearized log-transformed equation. Other studies incorrectly reported
parameters as mm-to-g conversions when they were in fact cm-to-g
conversions. We standardized each study by converting coefficients and
report all parameters as TL(mm) to TW (g) conversions. Locations where
allometric studies have been performed are shown in Figure \ref{fig:map}
and summarized in Table \ref{tab:all_params}.

We obtained a total of 18 parameter pairs by combining length-weight
parameters extracted from the literature and the additional pair
calculated here. Recall that the objective of this study is not to
describe population-level variations, but rather to estimate how the use
of \emph{ex situ} parameters influences weight estimates. We used the
central Mexican Caribbean as a case study of how the use of \emph{ex
situ} parameters influences the accuracy of weight estimates for
lionfish. We estimated \(TW\) from the \(TL\) observations we collected
in the central Mexican Caribbean (n = 109, with \(TL\) ranging from 34
mm to 310 mm) using each of the 18 parameter pairs and divided predicted
weights by known observed weights to obtain a simple measure of over- or
underestimation. Difference in mean weight ratios were tested with an
analysis of covariance (ANCOVA) using study and \(TL\) as covariates.
Ratios were logit-transformed prior to analysis, and a \emph{post-hoc}
Tukey's test was used to identify groups where mean ratios did not
differ. All analyses were performed in R version 3.5.2
\citep{rcore_2018}. Raw data and code used in this work are available on
github at github.com/jcvdav/lionfish\_biometry.

@@

The length-weight relationship for organisms from the central Mexican
Caribbean resulted in the coefficient values
\(a = 3.2056297\times 10^{-6}\), \(b = 3.2347391\) and
\(c = -5.4940866\) (\(R^2 = 0.977\), F(df = 1; 107) = 6928.67,
\(p < 0.001\)). The allometric factor (\(b\)) was significantly
different from \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicating that
lionfish present allometric growth. The length-weight coefficients
estimated in this study were within the range identified by studies in
other regions (Table \ref{tab:all_params}). Figure \ref{fig:l-w-carib}
shows the relationship between TL and TW for this region.

@@

There were significant differences in our predicted weights for the
central Mexican Caribbean when using each of the different pairs of
parameters (\(F(df = 17; 1944) = 61.55; p < 0.001\)). The lowest weight
estimates for the observed lengths resulted from using the allometric
parameters from Banco Chinchorro in the Caribbean, with mean \(\pm\) SD
of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In contrast, the
highest weight estimates came from the Western Atlantic with 73.76
\(\pm\) 96.11 g \citep{barbour_2011}. To put this in context, true
observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weigths predicted
from these extreme parameters correspond to mean \(\pm\) SD
predicted-to-observed weights ratios of 0.80 \(\pm\) 0.19 and 1.76
\(\pm\) 0.50 (mean \(\pm\) SD), respectively. At its extremes, other
parameters resulted in under- and overestimations in the order of 0.36
to 3.51 of the actual observed weight, indicating that \emph{ex situ}
parameters can result in substantial weight under- and overestimation.

Tukey's \emph{post-hoc} test suggests that weight ratios for the central
Mexican Caribbean were not different from those obtained with parameters
from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico
(Tukey's HSD \(p > 0.05\)). Weight estimates using parameters from the
Gulf of Mexico and Western Atlantic were higher on average than those
from the Caribbean (Fig \ref{fig:all_allo}). The average (\(\pm\) SD)
predicted-to-observed weight ratios from these three regions were 1.24
\(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
Predicted-to-observed weight ratios are presented in Figure
\ref{fig:bio_ratio}.

@@

\caption{\label{tab:unnamed-chunk-7}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
\centering
\begin{tabular}{llllrll}
\toprule
Region & Sex & n & a & b & \$R\textasciicircum{}2\$ & Reference\\
\midrule
Western Atlantic & B & 774 & 2.9 & 2.89 & - & Barbour et al., 2011\\
Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
\addlinespace
GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
Caribbean & B & 458 & 3.6 & 2.81 & - & Sandel et al., 2015\\
\addlinespace
Caribbean & B & 419 & 2.8 & 2.85 & 0.87 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.3 & 2.89 & 0.92 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.3 & 3.24 & 0.97 & Edwards et al., 2014\\
Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.8 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
\addlinespace
Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/fit2-1.pdf}
\caption{\label{fig:all_allo}log-log transformation of the length-weight
relationships (n = 18) for 12 studies and this study. The curves are
shown for the range of lengths reported in each study (See Supplementary
Table 2); when ranges were not present, we use the ones found in this
study (34mm - 310 mm). Colors indicate studies from which the parameters
were extracted. Dotted, dashed and solid lines show models for males,
females, and combined sexes, respectively. The dashed black line
represents the relationship estimated in this study. There are two solid
green lines for Sabido-Itza et al, 2016b, one for each of the two sites
for which they report parameters. A log-log version of this figure is
presented in Figure S4.}
\end{figure}

@@

Our results suggest that lionfish exhibit highly variable allometric
relationships across the invaded range, and that this variation is
spatially heterogeneous and relevant for management of the invasion.
Moreover, we show that the use of \emph{ex situ} parameters may lead to
highly biased weight estimates. Our comparison of observed weights to
those predicted with locally-informed parameters and \emph{ex situ}
parameters showed that weight can be overestimated by more than a
three-fold, and highlights the need to use local information. Here we
discuss the implications of our findings and highlight potential future
research directions.

@@

We detected substantial differences in weight-at-length between
organisms from the Caribbean, Gulf of Mexico, and Western Atlantic.
Groupings of predicted-to-observed weight ratios identified in our
\emph{post hoc} testing aligned with the spatial distribution of the
examined studies, suggesting that these differences may be mediated by
space. These regional allometric differences mirror similar patterns in
age-at-length of lionfish across both their invaded and native regions
\citep{pusack_2016}. Variation may be driven by genetics or by
organisms' exposure to distinct environmental conditions. For example,
\citet{betancurr_2011} used mitochondrial DNA to demonstrate the
existence of two distinct population groups, identified as the
``Caribbean group'' and ``Northern Group'', and \citet{fogg_2015}
alternatively suggested that age-at-length differences may be driven by
the environment.

We might be inclined to attribute all variation to the spatial origin of
these parameters. However, these were not only collected for different
locations, but also using a range of different sampling methods and for
different points in time (See Supplementary Table 2 for an extended
version of Table 1). While we are not able to evaluate how these factors
influence previous estimates (raw data from all studies would be
needed), it is certain that the lack of locally-calculated parameters
may induce significant bias when calculating weight from length
observations. Differences in weight-at-length could also reflect
differential energy input or usage, or a combination of both. The
magnitude of the bias and our lack of understanding of the source of
variation hihglights the need to simultaneously collect length-weight
information across the invaded range to test for spatially-induced
patterns and link these to previously suggested environmental and
genetic structures. Such an endeavor would provide insights into
lionfish biology and better inform management.

Applying parameters estimates to lengths that may be outside the range
of lengths originally used to estimate the parameters may also induce
variation lead to over- and underestimation. Our smallest observed
length was for an organism 34 mm in TL. However, only two studies
estimated parametrs with smaller organisms
\citep{sabidoitza_2016,edwards_2014}. On the other hand, our largest
organism had a TL of 310 mm, which is well within the range of all other
studies (maximum observed lengths varied from 325 mm to 475 mm; See
Supplementary Table 2). Due to the exponential nature of the allometric
relationship, the error is higher when extrapolation is done for TLs
that are larger than the maximum. This means that not only must managers
use locally-informed data, but that these local data must also include
the full range of lengths present in the region to reduce error caused
by extrapolation.

The results presented here have fundamental implications for management.
For example, \citet{edwards_2014} simulated a lionfish culling program
under two scenarios, one using length-at-age and length-to-weight
parameters from North Carolina and one using parameters from Little
Cayman. Their results show that using different parameters caused up to
a four-year difference in the time required for the simulated lionfish
population to recover to 90\% of its initial biomass after removals
ceased. Here, we show that using one set of length-weight parameters
versus another for a given length can result in more than a threefold
under- or overestimation of total weight. These spatially-driven
differences become especially important when allocating resources for
lionfish removal programs, incentivizing lionfish fisheries as a source
of alternative livelihoods, or estimating ecosystem impacts. Research
efforts focused on invasive lionfish populations need to use parameters
calculated for their region to the extent possible, or at least use
reasonable sets of different parameters that provide upper and lower
bounds in their results.

>>>>

\begin{abstract}
Lionfish (\textit{Pterois volitans / miles}) are an invasive species in
the Western Atlantic and the Caribbean. Improving management of invasive
lionfish populations requires accurate total biomass estimates, which
depend on accurate estimates of allometric growth. Sedentary species
like lionfish often exhibit high levels of spatial variation in life
history characteristics. We review 17 published length-weight
relationships for lionfish taken throughout their invasive range and
found regional differences that led to significant under- and
overestimation of weight estimates. The spatial pattern we observed is
consistent with findings from other studies focusing on genetics or
length-at-age. We show that the use of \textit{ex situ} parameters can
result in up to a threefold under- or overestimation of total weight,
but using parameters from nearby regions reduces this error. These
findings can have substantial implications for management in terms of
predicting effects on local ecosystems, evaluating the effectiveness of
removal programs, or estimating biomass available for harvest.
\end{abstract}

@@

Outcomes of previous studies suggest lionfish are likely to exhibit
spatial heterogeneity in the length-weight relationship, which we
summarize in two main causes. First, culling programs are effective in
reducing local adult populations largely because lionfish exhibit high
levels of site fidelity and small home ranges
\citep{Fishelson_1997,kochzius_2005,jud_2012,cote_2014}. It is known
that fish with sedentary behavior are likely to exhibit high levels of
spatial variation in important life history characteristics such as
growth or natural mortality rates
\citep{gunderson_2008,hutchinson_2008,wilson_2012,guan_2013}. Second,
genetic analysis of lionfish suggests biological differences due to the
existence of two genetically distinct invasive subpopulations between
the Western Atlantic and the Caribbean \citep{betancurr_2011}. The large
number of site-specific studies reporting the length-weight relationship
of lionfish provide variable estimates. These differences may be
increasingly important when estimating the potential effectiveness of
lionfish culling programs
\citep{barbour_2011,morris_2011,cote_2014,johnston_2015}. However, the
magnitude of the error caused by using \emph{ex situ} parameters to
estimate total weight from length observations remains unexplored.

@@

We reviewed 12 published studies and obtained 17 length-weight
relationships for the Western Atlantic (n = 2), Gulf of Mexico (n = 7),
and Caribbean (n = 8, Table \ref{tab:all_params}, Fig \ref{fig:map}). We
collected information on sex differentiation, location, length and depth
ranges and sampling methods from each study when available. Only two
studies reported parameters for each gender
\citep{aguilarperera_2016,fogg_2013}, so we assumed both genders were
included in a study if gender was unspecified. Reviewed studies
presented information for organisms ranging between 25 mm and 475 mm in
Total Length (\(TL\)), and that were obtained at depths between 0.5 m
and 57 m. Four studies explicitly stated that their organisms were
sampled with pole spears
\citep{dahl_2014,aguilarperera_2016,chin_2016,sabidoitz_2016}, and six
studies mentioned that some of their organisms were obtained with pole
spears (or other type of harpoon) but also hand-held nets or fish traps
\citep{barbour_2011,fogg_2013,edwards_2014,toledohernndez_2014,sandel_2015,sabidoitza_2016},
and two studies did not specify how organisms were sampled
\citep{darling_2011,deleon_2013}.

@@

Some of the reviewed studies inconsistently defined \(a\) as either the
ponderal index from Eq. \ref{eq:allometric} or the y-intercept from the
linearized log-transformed equation. Other studies incorrectly reported
parameters as mm-to-g conversions when they were in fact cm-to-g
conversions. We standardized each study by converting coefficients and
report all parameters as TL (mm) to TW (g) conversions. Locations where
allometric studies have been performed are shown in Figure \ref{fig:map}
and summarized in Table \ref{tab:all_params}.

We obtained a total of 18 parameter pairs by combining length-weight
parameters extracted from the literature and the additional pair
calculated here. Recall that the objective of this study is not to
describe variations between populations, but rather to estimate how the
use of \emph{ex situ} parameters influences weight estimates. We used
the central Mexican Caribbean as a case study of how the use of \emph{ex
situ} parameters influences the accuracy of weight estimates for
lionfish. We estimated \(TW\) from the \(TL\) observations we collected
in the central Mexican Caribbean (n = 109, with \(TL\) ranging from 34
mm to 310 mm) using each of the 18 parameter pairs and divided predicted
weights by known observed weights to obtain a simple measure of over- or
underestimation. Difference in mean weight ratios were tested with an
analysis of covariance (ANCOVA), where the sources of variation were the
study and \(TL\). Ratios were logit-transformed prior to analysis, and a
\emph{post-hoc} Tukey's test was used to identify groups where mean
ratios did not differ. All analyses were performed in R version 3.5.2
\citep{rcore_2018}. Raw data and code used in this work are available on
github at github.com/jcvdav/lionfish\_biometry.

@@

The length-weight relationship for organisms from the central Mexican
Caribbean resulted in coefficient values of
\(a = 3.2056297\times 10^{-6}\) and \(b = 3.2347391\) (\(R^2 = 0.977\),
F(df = 1; 107) = 6928.67, \(p < 0.001\)). The allometric factor (\(b\))
was significantly different from \(b = 3\) (\(t(107) = 6.04; p<0.001\))
corroborating that lionfish present allometric growth. The length-weight
coefficients estimated in this study were within the range identified by
studies in other regions (Table \ref{tab:all_params}). Figure
\ref{fig:l-w-carib} shows the relationship between TL and TW for this
region.

@@

There were significant differences in our predicted weights for the
central Mexican Caribbean when using each of the different pairs of
parameters (\(F(df = 17; 1943) = 24.96; p < 0.001\)). The lowest weight
estimates for the observed lengths resulted from using the allometric
parameters from Banco Chinchorro in the Caribbean, with mean \(\pm\) SD
of 40.37 \(\pm\) 58.74 g \citep{sabidoitz_2016}. In contrast, the
highest weight estimates came from the Western Atlantic with 73.76
\(\pm\) 96.11 g \citep{barbour_2011}. To put this in context, true
observed weights have a mean of 52.56 \(\pm\) 76.58 g. Weights predicted
from these extreme parameters correspond to mean \(\pm\) SD
predicted-to-observed weights ratios of 0.80 \(\pm\) 0.19 and 1.76
\(\pm\) 0.50 (mean \(\pm\) SD), respectively. The largest under- and
overestimations resulted in ratios of 0.36 and 3.51 of the actual
observed weight, indicating that \emph{ex situ} parameters can result in
substantial weight under- and overestimation.

Tukey's \emph{post-hoc} test suggests that weight ratios for the central
Mexican Caribbean were not different from those obtained with parameters
from Little Cayman, the Bahamas, and some sites in the Gulf of Mexico
(Tukey's HSD \(p > 0.05\)). Weight estimates using parameters from the
Gulf of Mexico and Western Atlantic were higher on average than those
from the Caribbean (Fig \ref{fig:all_allo}). The average (\(\pm\) SD)
predicted-to-observed weight ratios from these three regions were 1.24
\(\pm\) 0.309, 1.76 \(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
This suggest that the smallest errors are observed when using parameters
other locations in the Caribbean. Predicted-to-observed weight ratios
are presented in Figure \ref{fig:bio_ratio}.

@@

\caption{\label{tab:unnamed-chunk-7}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter (presented in $\times 10^{-5}$), b = exponent.}
\centering
\begin{tabular}{llllrll}
\toprule
Region & Sex & n & a & b & $R^2$ & Reference\\
\midrule
Western Atlantic & B & 774 & 2.9 & 2.89 & - & Barbour et al., 2011\\
Western Atlantic & B & - & 0.25 & 3.29 & - & Darling et al., 2011\\
GoM & B & 934 & 0.21 & 3.34 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
\addlinespace
GoM & M & 59 & 0.42 & 3.23 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & 0.99 & Fogg et al., 2013\\
GoM & M & 119 & 0.27 & 3.31 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & 0.94 & Fogg et al., 2013\\
Caribbean & B & 458 & 3.6 & 2.81 & - & Sandel et al., 2015\\
\addlinespace
Caribbean & B & 419 & 2.8 & 2.85 & 0.87 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.3 & 2.89 & 0.92 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.3 & 3.24 & 0.97 & Edwards et al., 2014\\
Caribbean & B & 2143 & 0.52 & 3.18 & 0.99 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.8 & 3.11 & 0.96 & Toledo-Hernández et al., 2014\\
\addlinespace
Caribbean & B & 449 & 0.23 & 3.25 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & 0.98 & This study\\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/fit2-1.pdf}
\caption{\label{fig:all_allo}Length-weight relationships (n = 18) for 12
studies and this study. The curves are shown for the range of lengths
reported in each study (See Supplementary Table 2); when ranges were not
present, we use the ones found in this study (34 mm - 310 mm). Colors
indicate studies from which the parameters were extracted. Dotted,
dashed, and solid lines show models for males, females, and combined
sexes, respectively. The dashed black line represents the relationship
estimated in this study. There are two solid green lines for Sabido-Itza
et al, 2016b, one for each of the two sites for which they report
parameters. A log-log version of this figure is presented in Figure S4.}
\end{figure}

@@

Our results suggest that lionfish exhibit highly variable allometric
relationships across the invaded range, and that this variation is
spatially heterogeneous and relevant for management of the invasion.
Moreover, we show that the use of \emph{ex situ} parameters may lead to
highly biased weight estimates. Our comparison of observed weights to
those predicted with locally-informed parameters and \emph{ex situ}
parameters showed that weight can be overestimated by more than a
three-fold, and highlights the need to use local information. Here we
discuss the implications of our findings, possible shortcommings in our
analyses, and highlight potential future research directions.

@@

We detected substantial differences in weight-at-length between
organisms from the Caribbean, Gulf of Mexico, and Western Atlantic.
Groupings of predicted-to-observed weight ratios identified in our
\emph{post hoc} testing aligned with the spatial distribution of the
examined studies, suggesting that these differences may be mediated by
space. These regional allometric differences mirror similar patterns in
length-at-age of lionfish across both their invaded and native regions
\citep{pusack_2016}. Variation may be driven by genetics or by
organisms' exposure to distinct environmental conditions. For example,
\citet{betancurr_2011} used mitochondrial DNA to demonstrate the
existence of two distinct population groups, identified as the
``Caribbean group'' and ``Northern Group'', and \citet{fogg_2015}
alternatively suggested that length-at-age differences may be driven by
the environment.

We might be inclined to attribute all variation to the spatial origin of
these parameters. However, these were not only collected for different
locations, but also using a range of different sampling methods and at
different points in time (See Supplementary Table 2 for an extended
version of Table 1). While we are not able to evaluate how these factors
influence previous estimates (raw data from all studies would be
needed), it is certain that the lack of locally-calculated parameters
may induce significant bias when calculating weight from length
observations. Differences in weight-at-length could also reflect
differential energy input or usage, or a combination of both. The
magnitude of the bias and our lack of understanding of the source of
variation highlights the need to simultaneously collect length-weight
information across the invaded range to test for spatially-induced
patterns and link these to previously suggested environmental and
genetic structures. Such an endeavor would provide insights into
lionfish biology and better inform management.

Applying parameters estimates to lengths outside the range of lengths
originally used to estimate the parameters may also induce error. Our
smallest observed organism was 34 mm in \(TL\), and only two studies
estimated parametrs with smaller organisms
\citep{sabidoitza_2016,edwards_2014}. On the other hand, our largest
organism had a \(TL\) of 310 mm, which is well within the range of all
other studies (maximum observed lengths varied from 325 mm to 475 mm;
See Supplementary Table 2). Due to the power-function describing the
allometric relationship, the error is higher when extrapolation is done
for lengths that are larger than the maximum length used to estimate the
parameters. This means that not only must managers use locally-informed
data, but that these local data must also include the full range of
lengths present in the region to reduce error caused by extrapolation.

The results presented here have fundamental implications for management.
For example, \citet{edwards_2014} simulated a lionfish culling program
under two scenarios, one using length-at-age and length-to-weight
parameters from North Carolina and one using parameters from Little
Cayman. Their results show that using different parameters caused up to
a four-year difference in the time required for the simulated lionfish
population to recover to 90\% of its initial biomass after removals
ceased. Here, we show that using one set of length-weight parameters
versus another for a given length can result in more than a threefold
under- or overestimation of total weight. These differences become
especially important when allocating resources for lionfish removal
programs, incentivizing lionfish fisheries as a source of alternative
livelihoods, or estimating ecosystem impacts. Research efforts focused
on invasive lionfish populations need to use parameters calculated for
their region to the extent possible, or at least use reasonable sets of
different parameters that provide upper and lower bounds in their
results.

### 2019-01-30 docs/reviews.Rmd
Proof-read and added the LaTexDiff version of the marked up MS

We appreciate the professional way in which our manuscript has been handled. Here we address the issues, suggestions, and comments raised by you and the reviewers. We include the original comment in plain text, and our responses in itallics.

@@

*We have included the url in the main text, but the decission to leave it there depends on the editorial formatting. However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the url to be incuded.*

@@

*Here we report the mean $\pm$ standard deviation of the estimated weights for the 109 organisms from the central Mexican Caribbean. We have modified the text to clearify our point.*

@@

*abido-Itza et al. 2016b report parameters from two locations in their study. We have included that information in the figure caption ("There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters"). The legend for Sex now shows distinct linetypes for Female and Males.*

@@

*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and data from Fogg et al. (2013) produced some of the largest estimates. After a careful evaulation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders. The corresponding modifications have been made in the text. Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*

@@

*As stated above, we have expanded on the role of these different sampling and processing methods and devoted a paragraph in the duscission (L175). We must clarify, however, that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2). The fact that similar comments were raised by Rev2 suggests that the text needed further clarification from our side. The objective of our study is not to describe the biological differences in length-weight relationshisp, but to estimate the effect that using ex situ parameter has and determine if this results in large errors.*

*We agree, however, that to estimate the "location effect" of the length-weight relationship, these should be modeled as a random effect. The GLMM would not only identify if differences exis, but also tell us the magnitude of these differences. This is a common approach in population biology and would in fact identify the random effect of the location in shaping the length-weight relationship. However, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data. We believe that after modifying the text to clearly state our objectives and including a discussion paragraph about this, we have addressed this concern.*

@@

In this manuscript, the authors present an analysis of 17 previously published weight-length relationships for lionfish throughout the species invasive range, along with new data on the weightlength relationship for a population along the central Mexican coast. The authors report important differences in allometric scaling among studies and highlight the effects of applying mis-specified growth parameters to stocks lacking this information. The overall question is relevant to fisheries management and control of invasive lionfish populations, and the paper is well referenced. However, there are several aspects of the paper that would improve the contribution, both in their methodological approach and discussion of their findings. I outline areas for major improvement below.

@@

Second, the parameter estimates from other studies are being applied to lengths of fish outside of the range of lengths that were used to generate the parameters. ANCOVA is the most powerful approach for comparing multiple linear relationships, as it specifically accounts for variation in the covariate (total length) among groups. The application of ANCOVA to the logtransformed weight-length relationships would identify if the beta (b) coefficient varied significantly among populations, and then which populations differed could be discerned using post-hoc tests.

@@

*As for the use of ANCOVA, this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates. As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations. However, we do not have the raw thata from other studies and applying this to the predicted estimates would not help us answer this question. In a sense, we would be asking if the lines in Fig 3 (whith no variation around them) have significantly different slopes and intercepts. As mentioned in the response to R1, we have included a discussion paragraph (L175) highlighting this.*

@@

*We have included all the information we collected from other studies in a supplementary table (Supplementary Table 2), an extention of Table 2, where other relevant variables are mentioned. Table 2 is now Table 1 after removing the regression table.*

@@

*That is correct, the 0.80 and 1.76 values make refrence to the mean ratios. We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51. We believe the new text now justifies including these extremes.*

>>>>

We appreciate the professional way in which our manuscript has been handled. Here we address the issues, suggestions, and comments raised by you and the reviewers. We include the original comment in plain text, and our responses in italics.

@@

*We have included the URL in the main text, but the decision to leave it there depends on the editorial formatting. However, PeerJ has an "Additional Information and Declarations" section with a subsection on "Data Availability", where we expect the URL to be included.*

@@

*Here we report the mean $\pm$ standard deviation of the estimated weights for the 109 organisms from the central Mexican Caribbean. We have modified the text to clarify our point.*

@@

*Sabido-Itza et al. 2016b report parameters from two locations in their study. We have included that information in the figure caption ("There are two solid green lines for Sabido-Itza et al, 2016b, one for each of the two sites for which they report parameters"). The legend for Sex now shows distinct line types for Female and Males.*

@@

*We also expected estimates from spineless weight to underestimate of total weight, however this wasn't the case, and data from Fogg et al. (2013) produced some of the largest estimates. After a careful evaluation of their paper, we noted that their Table 1, in fact, reports TW to TL conversions by gender and for pooled genders. The corresponding modifications have been made in the text. Their paper can be found in this link: https://lionfish.co/wp-content/uploads/2013/05/Distribution-of-Lionfish-in-the-Gulf-of-Mexico.pdf*

@@

*As stated above, we have expanded on the role of these different sampling and processing methods and devoted a paragraph in the discussion (L175). We must clarify, however, that our OLS regression was only performed to estimate the length-weight relationship for the 109 organisms from the central Mexican Caribbean (Fig 2). The fact that similar comments were raised by Rev2 suggests that the text needed further clarification from our side. The objective of our study is not to describe the biological differences in length-weight relationships, but to estimate the effect that using ex situ parameter has and determine if this results in large errors.*

*We agree, however, that to estimate the "location effect" of the length-weight relationship, these should be modeled as a random effect. The GLMM would not only identify if differences exist, but also tell us the magnitude of these differences. This is a common approach in population biology and would in fact identify the random effect of the location in shaping the length-weight relationship. However, for this we would need to either have the raw data from all the reviewed studies or perform a region-wide collection that would allow us to have standardized data. We believe that after modifying the text to clearly state our objectives and including a discussion paragraph about this, we have addressed this concern.*

@@

In this manuscript, the authors present an analysis of 17 previously published weight-length relationships for lionfish throughout the species invasive range, along with new data on the length-weight relationship for a population along the central Mexican coast. The authors report important differences in allometric scaling among studies and highlight the effects of applying mis-specified growth parameters to stocks lacking this information. The overall question is relevant to fisheries management and control of invasive lionfish populations, and the paper is well referenced. However, there are several aspects of the paper that would improve the contribution, both in their methodological approach and discussion of their findings. I outline areas for major improvement below.

@@

Second, the parameter estimates from other studies are being applied to lengths of fish outside of the range of lengths that were used to generate the parameters. ANCOVA is the most powerful approach for comparing multiple linear relationships, as it specifically accounts for variation in the covariate (total length) among groups. The application of ANCOVA to the log-transformed weight-length relationships would identify if the beta (b) coefficient varied significantly among populations, and then which populations differed could be discerned using post-hoc tests.

@@

*As for the use of ANCOVA, this is a similar comment to that raised by Rev1, who suggested the use of a GLMM with locations as random effects that induce variation in the length-weight estimates. As in that case, we agree that an ANCOVA applied to the raw length-weight information would identify if differences exist between locations. However, we do not have the raw data from other studies and applying this to the predicted estimates would not help us answer this question. In a sense, we would be asking if the lines in Fig 3 (with no variation around them) have significantly different slopes and intercepts. As mentioned in the response to R1, we have included a discussion paragraph (L175) highlighting this.*

@@

*We have included all the information we collected from other studies in a supplementary table (Supplementary Table 2), an extension of Table 2, where other relevant variables are mentioned. Table 2 is now Table 1 after removing the regression table.*

@@

*That is correct, the 0.80 and 1.76 values make reference to the mean ratios. We have modified the text to make this clear, but believe that it is important to explicitly state that the maximum under- and overestimations were by a factor of 0.36 and 3.51. We believe the new text now justifies including these extremes.*
